\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Draft of response to the editor

\section*{Response to the Editor's Report}
\def\thesection{E}
\begin{rebuttal} %\setcounter{enumi}{-1}
\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.}

\item \reviewtext{The reviewers feel the paper interesting, which many include publishable materials. On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g. introduction etc.), and highlight the novelty and contribution. Also the relevance of the paper to the journal should be clarified.}

\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.  If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
more than 8 double-column pages using IEEE template.}

\item \reviewtext{In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.

@@

>>>>

\section*{Response to the Editor's Report}
\def\thesection{E}
\begin{rebuttal} %\setcounter{enumi}{-1}
\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.

The reviewers feel the paper interesting, which many include publishable materials. On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g. introduction etc.), and highlight the novelty and contribution. Also the relevance of the paper to the journal should be clarified.}

Thank you for the response. We have undertaken a large overhaul of the manuscript in order to accomodate for the suggested changes of the reviewers. The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it. We state the estimation problem tackled, namely, range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches. We believe that the more clarified novelty and contribution also better justifies the relevance of the paper to the TAC journal.

\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.  If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
more than 8 double-column pages using IEEE template.

In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.

@@

After a large revision of our manuscript, including the suggested additions and modifications from the reviewers, we have rearranged and greatly shortened the work (in particular the introduction and cryptography sections, but all sections have been partially modified to be clearer). Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again. We hope that this decision is made clearer from the newly revised and rearranged manuscript. Below, we have detailed how each of the reviewer comments have been taken into account when revising the work.
